### 2022-05-20 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@fb8b223211b9147a644676f6ddaec4102610bd72 🚀

Ecological networks are a backbone for key ecological and evolutionary
processes; yet enumerating all of the interactions between \(S\) species
is a daunting task, as it scales with \(S^2\), \emph{i.e.} the squared
species richness (\textbf{Martinez1992ConCon?}). Recent contributions to
the field of ecological network prediction (Pichler et al., 2020;
Strydom et al., 2021; \textbf{Becker2022OptPre?}) highlight that
although interactions can be predicted by adding ecologically relevant
information (in the form of, \emph{e.g.} traits), we do not have robust
guidelines as to how the predictive ability of these models should be
evaluated, nor about how the models should be trained. Here, by relying
on simple derivations and a series of simulations, we formulate a number
of such guidelines, specifically for the case of binary classifiers
derived from thresholded values. Specifically, we conduct an
investigation of the models in terms of their skill (ability to make the
right prediction), bias (trends towards systematically over-predicting
one class), class imbalance (the relative number of cases representing
interactions), and show how these effects interact. We conclude on the
fact that models with the best interaction-scale predictive score do not
necessarily result in the most accurate representation of the network.

@@

Species interaction networks are often under-sampled (Jordano, 2016b,
2016a), and this under-sampling is structured taxonomically (Beauchesne
et al., 2016), structurally (de Aguiar et al., 2019) and spatially
(Poisot, Bergeron, et al., 2021; Wood et al., 2015). As a consequence,
networks suffer from data deficiencies both within and between datasets.
This implies that the comparison of classifiers across space, when
undersampling varies locally (see \emph{e.g.} McLeod et al., 2021) is
non-trivial. Furthermore, the baseline value of classifiers performance
measures under various conditions of skill, bias, and prevalence, has to
be identified to allow researchers to evaluate whether their interaction
prediction model is indeed learning. Taken together, these
considerations highlight three specific issues for ecological networks.
First, what values of performance measures are indicative of a
classifier with no skill? This is particularly important as it can
evaluate whether low prevalence can lull us into a false sense of
predictive accuracy. Second, independently of the question of model
evaluation, is low prevalence an issue for \emph{training} or
\emph{testing}, and can we remedy it? Finally, because the low amount of
data on interaction makes a lot of imbalance correction methods (see
\emph{e.g.} Branco et al., 2015) hard to apply, which indicators can be
optimized by sacrificing least amount of positive interaction data?

@@

\begin{figure}
\hypertarget{fig:bias}{%
\centering
\includegraphics{figures/changing-bias.png}
\caption{Consequences of changing the classifier skills (\(s\)) and bias
(\(s\)) for a connectance \(\rho=0.15\), on accuracy, \(F_1\), postive
predictive value, and \(\kappa\). Accuracy increases with skill, but
also increases when the bias tends towards estimating \emph{fewer}
interactions. The \(F_1\) score increases with skill but also increases
when the bias tends towards estimating \emph{more} interactions; PPV
behaves in the same way. Interestingly, \(\kappa\) responds as expected
to skill (being negative whenever \(s < 0.5\)), and peaks for values of
\(b \approx 0.5\); nevertheless, the value of bias for which \(\kappa\)
is maximized in \emph{not} \(b=0.5\), but instead increases with
classifier skill. In other words, at equal skill, maximizing \(\kappa\)
would lead to select a \emph{more} biased classifier.}\label{fig:bias}
}
\end{figure}

In fig.~\ref{fig:bias}, we show that none of the four measures satisfy
all the considerations at once: \(F_1\) increases with skill, and
increases monotonously with bias; this is because \(F_1\) does not
account for true negatives, and the increase in positive detection masks
the over-prediction of interactions. Informedness varies with skill,
reaching 0 for a no-skill classifier, but is entirely unsensitive to
bias. Both MCC and \(\kappa\) have the same behavior, whereby they
increase with skill. \(\kappa\) peaks at increasing values of biass for
increasing skill, \emph{i.e.} is likely to lead to the selection of a
classifier that over-predicts interactions. By contract, MCC peaks at
the same value, regardless of skill, but this value is not
\(\text{logit}(b)=0\): unless at very high classifier skill, MCC risks
leading to a model that over-predicts interactions. In
fig.~\ref{fig:connectance}, we show that all measures except \(F_1\)
give a value of 0 for a no-skill classifier, and are forced towars their
correct maximal value when skill changes (\emph{i.e.} a more connected
networks will have higher values for a skilled classifierd, and lower
values for a classifier making mostly mistakes).

@@

The dataset used for numerical experiments is composed of a grid of 35
values of connectance (from 0.011 to 0.5) and 35 values of \(\nu\) (from
0.02 to 0.98); for each pair of values, 500 networks are generated and
predicted. For each network, we train four machines: a trait-based k-NN
(\emph{e.g.} \textbf{Desjardins-Proulx2017EcoInt?}), a regression tree,
a regression random forest, and a boosted regression tree. Following
results from Pichler et al. (2020), linear models have not been
considered (in any way, the relationship in the simulated networks is
non-linear). The point of these numerical experiments is \emph{not} to
recommend the best model (this is likely problem-specific), but to
highlight a series of recommendations that would work for supervised
learning tasks. All models were taken from the \texttt{MLJ.jl} package
(Blaom et al., 2020; Blaom \& Vollmer, 2020) in Julia 1.7 (Bezanson et
al., 2017). All machines use the default parameterization; this is an
obvious deviation from best practices, as the hyperparameters of any
machine require training before its application on a real dataset. As we
use 612500 such datasets, this would require over 2 millions unique
instances of tweaking the hyperparameters, which is prohibitive from a
computing time point of view. An important thing to keep in mind is that
the problem we simulate has been designed to be simple to solve: we
expect all machines with sensible default parameters to fare well ---
the results presented in the later sections show that this assumption is
warranted, and we further checked that the models do not overfit by
ensuring that there is never more than 5\% of difference between the
accuracy on the training and testing sets. All machines return a
quantitative prediction, usually (but not necessarily) in \([0,1]\),
which is proportional (but not necessarily linearly) to the probability
of an interaction between \(i\) and \(j\). The ROC-AUC and PR-AUC (and
therefore the thresholds) can be measured by integrating over the domain
of the values return by each machine, but in order to make the
average-based ensemble model more meaningful, all predictions are
expressed in \([0,1]\).

@@

\begin{figure}
\hypertarget{fig:optimvalue}{%
\centering
\includegraphics{figures/optimal_value.png}
\caption{When trained on their optimally biased training set, most
models were able to maximize their performance; this is not true for
decision tree, which had a very low PR-AUC, and to some extent for ridge
regression who had a slow increase with network connectance. The
ensemble had a consistently high performance despite incorporating poor
models.}\label{fig:optimvalue}
}
\end{figure}

When trained at their optimal training set balance, connectance still
had a significant impact on the performance of some machines
fig.~\ref{fig:optimvalue}. Notably, Decision Tree, Random Forest, and
Ridge Regression had low values of PR-AUC. In all cases, the Boosted
Regression Tree was reaching very good predictions (especially for
connectances larger than 0.1), and the ensemble was almost always
scoring perfectly. This suggests that all the models are biased in
different ways, and that the averaging in the ensemble is able to
correct these biases. We do not expect this last result to have any
generality, and provide a discussion of a recent example in which the
ensemble was performing worse than its components models.

@@

In this last section, we generate a network using the same model as
before, with \(S_1, S_2 = 50, 80\) species, a connectance of
\(\approx 0.16\) (\(\xi = 0.19\)), and a training set balance of
\(0.5\), as fig.~\ref{fig:optimbias} suggests this is the optimal
training set balance for this range of connectance. The prediction made
on the complete dataset is presented in fig.~\ref{fig:ecovalid}.
Visualizing the results this way highlights the importance of
exploratory data analysis: whereas all models return a network with
interactions laying mostly on the diagonal (as expected), the Ridge
Regression is quite obviously biased. Despite this, we can see that the
ensemble is close to the initial dataset.

@@

\hypertarget{tbl:comparison}{}
\begin{longtable}[]{@{}rccccccc@{}}
\caption{\label{tbl:comparison}Values of four performance metrics, and
five network structure metrics, for 500 independent predictions similar
to the ones presented in fig.~\ref{fig:ecovalid}. The values in
\textbf{bold} indicate the best value for each column (including ties).
Because the values have been rounded, values of 1.0 for the ROC-AUC
column indicate an average \(\ge 0.99\).}\tabularnewline
\toprule
Model & MCC & Inf. & ROC-AUC & PR-AUC & Conn. & \(\eta\) &
\(Q\)\tabularnewline
\midrule
\endfirsthead
\toprule
Model & MCC & Inf. & ROC-AUC & PR-AUC & Conn. & \(\eta\) &
\(Q\)\tabularnewline
\midrule
\endhead
Decision tree & 0.85 & 0.92 & 0.97 & 0.12 & 0.21 & 0.76 &
0.31\tabularnewline
BRT & \textbf{0.90} & 0.90 & 0.98 & 0.86 & 0.23 & 0.82 &
0.27\tabularnewline
Random Forest & \textbf{0.90} & \textbf{0.96} & \textbf{1.00} & 0.27 &
\textbf{0.20} & \textbf{0.72} & \textbf{0.32}\tabularnewline
Ridge Regression & 0.80 & 0.91 & 0.95 & 0.58 & 0.24 & 1.0 &
0.18\tabularnewline
Ensemble & 0.88 & 0.94 & \textbf{1.00} & \textbf{0.96} & \textbf{0.20} &
0.75 & 0.31\tabularnewline
Data & & & & & 0.18 & 0.66 & 0.34\tabularnewline
\bottomrule
\end{longtable}

@@

It is noteworthy that the ensemble model was systematically better than
the component models. We do not expect that ensembles will \emph{always}
be better than single models. Networks with different structures than
the one we simulated here may respond in different ways, especially if
the rules are fuzzier than the simple rule we used here. In a recent
multi-model comparison involving supervised and unsupervised learning,
(\textbf{Becker2022OptPre?}) found that the ensemble was \emph{not} the
best model. There is no general conclusion to draw from this besides
reinforcing the need to be pragmatic about which models should be
included in the ensemble, or whether to use an ensemble at all. In a
sense, the surprising performance of the ensemble model should form the
basis of the last recommendation: optimal training set balance and its
interaction with connectance and the specific binary classifier used is,
in a sense, an hyperparameter that should be assessed. The distribution
of results in fig.~\ref{fig:optimbias} and fig.~\ref{fig:optimvalue}
show that there are variations around the trend. TODO fix this sentence

@@

Thirdly, regardless of network connectance, maximizing informedness
required a training set balance of about 0.5, and maximizing the MCC
required a training set bias of 0.7 and more. This has an important
consequence in ecological networks, for which the pool of positive cases
(interactions) to draw from is typically small: the most parsimonious
measure (\emph{i.e.} the one requiring to discard the least amount of
information to train the model) will give the best validation potential,
and is probably the informedness (maximizing informedness is the
generally accepted default for imbalanced classification; Schisterman et
al., 2005).

One key element for real-life data that can make the prediction exercise
more tractable is that some interactions can safely be assumed to be
impossible; indeed, a lot of networks admit a stochastic block model as
a good approximation (\emph{e.g.} \textbf{Xie2017ComCom?}). In
ecological networks, this can be due to spatial constrains
(\textbf{Valdovinos2019MutNet?}), or to the long-standing knowledge that
some links are ``forbidden'' due to traits (\textbf{Olesen2011MisFor?})
or abundances (\textbf{Canard2014EmpEva?}). The matching rules
(\textbf{Strona2017ForPer?}) can be incorporated in the model either by
adding compatibility traits, or by \emph{only} training the model on
pairs of species that are not likely to be forbidden links. Besides
forbidden links, a real-life case that may arise is multi-interaction or
multi-layer networks (\textbf{Pilosof2017MulNat?}). These can be studied
using the same general approach outlined here, either by assuming that
pairs of species can interact in more than one way (wherein one would
train a model for each type of interaction, based on the relevant
predictors), or by assuming that pairs of species can only have one type
of interaction (wherein this becomes a multi-label classification
problem).

@@

\leavevmode\hypertarget{ref-Beauchesne2016ThiOut}{}%
Beauchesne, D., Desjardins-Proulx, Archambault, P., \& Gravel, D.
(2016). Thinking Outside the Boxpredicting Biotic Interactions in
Data-poor Environments. \emph{Vie Et Milieu-Life and enVironment},
\emph{66}(3-4), 333--342.

@@

\leavevmode\hypertarget{ref-Blaom2020FleMod}{}%
Blaom, A. D., \& Vollmer, S. J. (2020). Flexible model composition in
machine learning and its implementation in MLJ. \emph{arXiv:2012.15505
{[}cs{]}}. \url{http://arxiv.org/abs/2012.15505}

@@

\leavevmode\hypertarget{ref-Branco2015SurPre}{}%
Branco, P., Torgo, L., \& Ribeiro, R. (2015). A Survey of Predictive
Modelling under Imbalanced Distributions. \emph{arXiv:1505.01658
{[}cs{]}}. \url{http://arxiv.org/abs/1505.01658}

@@

@@

\leavevmode\hypertarget{ref-Jeni2013FacImb}{}%
Jeni, L. A., Cohn, J. F., \& De La Torre, F. (2013). Facing Imbalanced
DataRecommendations for the Use of Performance Metrics. \emph{2013
Humaine Association Conference on Affective Computing and Intelligent
Interaction}, 245--251. \url{https://doi.org/10.1109/ACII.2013.47}

@@

@@

\leavevmode\hypertarget{ref-Pichler2020MacLea}{}%
Pichler, M., Boreux, V., Klein, A.-M., Schleuning, M., \& Hartig, F.
(2020). Machine learning algorithms to infer trait-matching and predict
species interactions in ecological networks. \emph{Methods in Ecology
and Evolution}, \emph{11}(2), 281--293.
\url{https://doi.org/10.1111/2041-210X.13329}

@@

\leavevmode\hypertarget{ref-Poisot2021ImpMam}{}%
Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J.
(2021). Imputing the mammalian virome with linear filtering and singular
value decomposition. \emph{arXiv:2105.14973 {[}q-Bio{]}}.
\url{http://arxiv.org/abs/2105.14973}

@@

\leavevmode\hypertarget{ref-Somodi2017PreDep}{}%
Somodi, I., Lepesi, N., \& Botta-Dukát, Z. (2017). Prevalence dependence
in model goodness measures with special emphasis on true skill
statistics. \emph{Ecology and Evolution}, \emph{7}(3), 863--872.
\url{https://doi.org/10.1002/ece3.2654}

@@

@@

@@

>>>>

Ecological networks are a backbone for key ecological and evolutionary
processes; yet enumerating all of the interactions between \(S\) species
is a daunting task, as it scales with \(S^2\), \emph{i.e.} the squared
species richness (Martinez, 1992). Recent contributions to the field of
ecological network prediction (Becker et al., 2022; Pichler et al.,
2020; Strydom et al., 2021) highlight that although interactions can be
predicted by adding ecologically relevant information (in the form of,
\emph{e.g.} traits), we do not have robust guidelines as to how the
predictive ability of these models should be evaluated, nor about how
the models should be trained. Here, by relying on simple derivations and
a series of simulations, we formulate a number of such guidelines,
specifically for the case of binary classifiers derived from thresholded
values. Specifically, we conduct an investigation of the models in terms
of their skill (ability to make the right prediction), bias (trends
towards systematically over-predicting one class), class imbalance (the
relative number of cases representing interactions), and show how these
effects interact. We conclude on the fact that models with the best
interaction-scale predictive score do not necessarily result in the most
accurate representation of the network.

@@

Species interaction networks are often under-sampled (Jordano, 2016a,
2016b), and this under-sampling is structured taxonomically (Beauchesne
et al., 2016), structurally (de Aguiar et al., 2019) and spatially
(Poisot, Bergeron, et al., 2021; Wood et al., 2015). As a consequence,
networks suffer from data deficiencies both within and between datasets.
This implies that the comparison of classifiers across space, when
undersampling varies locally (see \emph{e.g.} McLeod et al., 2021) is
non-trivial. Furthermore, the baseline value of classifiers performance
measures under various conditions of skill, bias, and prevalence, has to
be identified to allow researchers to evaluate whether their interaction
prediction model is indeed learning. Taken together, these
considerations highlight three specific issues for ecological networks.
First, what values of performance measures are indicative of a
classifier with no skill? This is particularly important as it can
evaluate whether low prevalence can lull us into a false sense of
predictive accuracy. Second, independently of the question of model
evaluation, is low prevalence an issue for \emph{training} or
\emph{testing}, and can we remedy it? Finally, because the low amount of
data on interaction makes a lot of imbalance correction methods (see
\emph{e.g.} Branco et al., 2015) hard to apply, which indicators can be
optimized by sacrificing least amount of positive interaction data?

@@

\begin{figure}
\hypertarget{fig:bias}{%
\centering
\includegraphics{figures/changing-bias.png}
\caption{Consequences of changing the classifier skills (\(s\)) and bias
(\(s\)) for a connectance \(\rho=0.15\), on \(F_1\), informedness, MCC,
and \(\kappa\). Accuracy increases with skill, but also increases when
the bias tends towards estimating \emph{fewer} interactions. The \(F_1\)
score increases with skill but also increases when the bias tends
towards estimating \emph{more} interactions. Interestingly, \(\kappa\)
responds as expected to skill (being negative whenever \(s < 0.5\)), and
peaks for values of \(b \approx 0.5\); nevertheless, the value of bias
for which \(\kappa\) is maximized in \emph{not} \(b=0.5\), but instead
increases with classifier skill. In other words, at equal skill,
maximizing \(\kappa\) would lead to select a \emph{more} biased
classifier.}\label{fig:bias}
}
\end{figure}

In fig.~\ref{fig:bias}, we show that none of the four measures satisfy
all the considerations at once: \(F_1\) increases with skill, and
increases monotonously with bias; this is because \(F_1\) does not
account for true negatives, and the increase in positive detection masks
the over-prediction of interactions. Informedness varies with skill,
reaching 0 for a no-skill classifier, but is entirely unsensitive to
bias. Both MCC and \(\kappa\) have the same behavior, whereby they
increase with skill. \(\kappa\) peaks at increasing values of bias for
increasing skill, \emph{i.e.} is likely to lead to the selection of a
classifier that over-predicts interactions. By contract, MCC peaks at
the same value, regardless of skill, but this value is not
\(\text{logit}(b)=0\): unless at very high classifier skill, MCC risks
leading to a model that over-predicts interactions. In
fig.~\ref{fig:connectance}, we show that all measures except \(F_1\)
give a value of 0 for a no-skill classifier, and are forced towars their
correct maximal value when skill changes (\emph{i.e.} a more connected
networks will have higher values for a skilled classifierd, and lower
values for a classifier making mostly mistakes).

@@

The dataset used for numerical experiments is composed of a grid of 35
values of connectance (from 0.011 to 0.5) and 35 values of \(\nu\) (from
0.02 to 0.98); for each pair of values, 500 networks are generated and
predicted. For each network, we train four machines: a trait-based k-NN
(\emph{e.g.} Desjardins-Proulx et al., 2017), a regression tree, a
regression random forest, and a boosted regression tree. Following
results from Pichler et al. (2020), linear models have not been
considered (in any way, the relationship in the simulated networks is
non-linear). The point of these numerical experiments is \emph{not} to
recommend the best model (this is likely problem-specific), but to
highlight a series of recommendations that would work for supervised
learning tasks. All models were taken from the \texttt{MLJ.jl} package
(Blaom et al., 2020; Blaom \& Vollmer, 2020) in Julia 1.7 (Bezanson et
al., 2017). All machines use the default parameterization; this is an
obvious deviation from best practices, as the hyperparameters of any
machine require training before its application on a real dataset. As we
use 612500 such datasets, this would require over 2 millions unique
instances of tweaking the hyperparameters, which is prohibitive from a
computing time point of view. An important thing to keep in mind is that
the problem we simulate has been designed to be simple to solve: we
expect all machines with sensible default parameters to fare well ---
the results presented in the later sections show that this assumption is
warranted, and we further checked that the models do not overfit by
ensuring that there is never more than 5\% of difference between the
accuracy on the training and testing sets. All machines return a
quantitative prediction, usually (but not necessarily) in \([0,1]\),
which is proportional (but not necessarily linearly) to the probability
of an interaction between \(i\) and \(j\). The ROC-AUC and PR-AUC (and
therefore the thresholds) can be measured by integrating over the domain
of the values return by each machine, but in order to make the
average-based ensemble model more meaningful, all predictions are
expressed in \([0,1]\).

@@

\begin{figure}
\hypertarget{fig:optimvalue}{%
\centering
\includegraphics{figures/optimal_value.png}
\caption{When trained on their optimally biased training set, most
models were able to maximize their performance; this is not true for
decision tree, k-NN, and to a lower extent RF. The ensemble had a
consistently high performance despite incorporating poor
models.}\label{fig:optimvalue}
}
\end{figure}

When trained at their optimal training set balance, connectance still
had a significant impact on the performance of some machines
fig.~\ref{fig:optimvalue}. Notably, Decision Tree, and k-NN, as well as
Random forest to a lower extent, had low values of PR-AUC. In all cases,
the Boosted Regression Tree was reaching very good predictions
(especially for connectances larger than 0.1), and the ensemble was
almost always scoring perfectly. This suggests that all the models are
biased in different ways, and that the averaging in the ensemble is able
to correct these biases. We do not expect this last result to have any
generality, and provide a discussion of a recent example in which the
ensemble was performing worse than its components models.

@@

In this last section, we generate a network using the same model as
before, with \(S_1, S_2 = 50, 80\) species, a connectance of
\(\approx 0.16\) (\(\xi = 0.19\)), and a training set balance of
\(0.5\), as fig.~\ref{fig:optimbias} suggests this is the optimal
training set balance for this range of connectance. The prediction made
on the complete dataset is presented in fig.~\ref{fig:ecovalid}.

@@

\hypertarget{tbl:comparison}{}
\begin{longtable}[]{@{}rccccccc@{}}
\caption{\label{tbl:comparison}Values of four performance metrics, and
five network structure metrics, for 500 independent predictions similar
to the ones presented in fig.~\ref{fig:ecovalid}. The values in
\textbf{bold} indicate the best value for each column (including ties).
Because the values have been rounded, values of 1.0 for the ROC-AUC
column indicate an average \(\ge 0.99\).}\tabularnewline
\toprule
Model & MCC & Inf. & ROC-AUC & PR-AUC & Conn. & \(\eta\) &
\(Q\)\tabularnewline
\midrule
\endfirsthead
\toprule
Model & MCC & Inf. & ROC-AUC & PR-AUC & Conn. & \(\eta\) &
\(Q\)\tabularnewline
\midrule
\endhead
Decision tree & 0.85 & 0.92 & 0.97 & 0.12 & 0.21 & 0.76 &
0.31\tabularnewline
BRT & \textbf{0.90} & 0.90 & 0.98 & 0.86 & 0.23 & 0.82 &
0.27\tabularnewline
Random Forest & \textbf{0.90} & \textbf{0.96} & \textbf{1.00} & 0.27 &
\textbf{0.20} & \textbf{0.72} & \textbf{0.32}\tabularnewline
k-NN & 0.80 & 0.91 & 0.95 & 0.58 & 0.24 & 1.0 & 0.18\tabularnewline
Ensemble & 0.88 & 0.94 & \textbf{1.00} & \textbf{0.96} & \textbf{0.20} &
0.75 & 0.31\tabularnewline
Data & & & & & 0.18 & 0.66 & 0.34\tabularnewline
\bottomrule
\end{longtable}

@@

It is noteworthy that the ensemble model was systematically better than
the component models. We do not expect that ensembles will \emph{always}
be better than single models. Networks with different structures than
the one we simulated here may respond in different ways, especially if
the rules are fuzzier than the simple rule we used here. In a recent
multi-model comparison involving supervised and unsupervised learning,
Becker et al. (2022) found that the ensemble was \emph{not} the best
model. There is no general conclusion to draw from this besides
reinforcing the need to be pragmatic about which models should be
included in the ensemble, or whether to use an ensemble at all. In a
sense, the surprising performance of the ensemble model should form the
basis of the last recommendation: optimal training set balance and its
interaction with connectance and the specific binary classifier used is,
in a sense, an hyperparameter that should be assessed. The distribution
of results in fig.~\ref{fig:optimbias} and fig.~\ref{fig:optimvalue}
show that there are variations around the trend. TODO fix this sentence

@@

Thirdly, regardless of network connectance, maximizing informedness
required a training set balance of about 0.5, and maximizing the MCC
required a training set bias of 0.7 and more. This has an important
consequence in ecological networks, for which the pool of positive cases
(interactions) to draw from is typically small: the most parsimonious
measure (\emph{i.e.} the one requiring to discard the least amount of
information to train the model) will give the best validation potential,
and is probably the informedness (maximizing informedness is the
generally accepted default for imbalanced classification; Schisterman et
al., 2005). This last result suggests that the amount of bias \emph{is}
an hyper-parameter that must be fine-tuned, as using the wrong bias can
lead to under-performing models.

One key element for real-life data that can make the prediction exercise
more tractable is that some interactions can safely be assumed to be
impossible; indeed, a lot of networks admit a stochastic block model as
a good approximation (\emph{e.g.} Xie et al., 2017). In ecological
networks, this can be due to spatial constrains (Valdovinos, 2019), or
to the long-standing knowledge that some links are ``forbidden'' due to
traits (Olesen et al., 2011) or abundances (Canard et al., 2014). The
matching rules (Olito \& Fox, 2015; Strona \& Veech, 2017) can be
incorporated in the model either by adding compatibility traits, or by
\emph{only} training the model on pairs of species that are not likely
to be forbidden links. Besides forbidden links, a real-life case that
may arise is multi-interaction or multi-layer networks (Pilosof et al.,
2017). These can be studied using the same general approach outlined
here, either by assuming that pairs of species can interact in more than
one way (wherein one would train a model for each type of interaction,
based on the relevant predictors), or by assuming that pairs of species
can only have one type of interaction (wherein this becomes a
multi-label classification problem).

@@

\leavevmode\hypertarget{ref-Beauchesne2016ThiOut}{}%
Beauchesne, D., Desjardins-Proulx, Archambault, P., \& Gravel, D.
(2016). Thinking Outside the Box--predicting Biotic Interactions in
Data-poor Environments. \emph{Vie Et Milieu-Life and enVironment},
\emph{66}(3-4), 333--342.

\leavevmode\hypertarget{ref-Becker2022OptPre}{}%
Becker, D. J., Albery, G. F., Sjodin, A. R., Poisot, T., Bergner, L. M.,
Chen, B., Cohen, L. E., Dallas, T. A., Eskew, E. A., Fagre, A. C.,
Farrell, M. J., Guth, S., Han, B. A., Simmons, N. B., Stock, M.,
Teeling, E. C., \& Carlson, C. J. (2022). Optimising predictive models
to prioritise viral discovery in zoonotic reservoirs. \emph{The Lancet
Microbe}. \url{https://doi.org/10.1016/S2666-5247(21)00245-7}

@@

\leavevmode\hypertarget{ref-Blaom2020FleMod}{}%
Blaom, A. D., \& Vollmer, S. J. (2020). \emph{Flexible model composition
in machine learning and its implementation in MLJ}.
\url{http://arxiv.org/abs/2012.15505}

@@

\leavevmode\hypertarget{ref-Branco2015SurPre}{}%
Branco, P., Torgo, L., \& Ribeiro, R. (2015). \emph{A Survey of
Predictive Modelling under Imbalanced Distributions}.
\url{http://arxiv.org/abs/1505.01658}

\leavevmode\hypertarget{ref-Canard2014EmpEva}{}%
Canard, E. F., Mouquet, N., Mouillot, D., Stanko, M., Miklisova, D., \&
Gravel, D. (2014). Empirical evaluation of neutral interactions in
host-parasite networks. \emph{The American Naturalist}, \emph{183}(4),
468--479. \url{https://doi.org/10.1086/675363}

@@

\leavevmode\hypertarget{ref-Desjardins-Proulx2017EcoInt}{}%
Desjardins-Proulx, P., Laigle, I., Poisot, T., \& Gravel, D. (2017).
Ecological interactions and the Netflix problem. \emph{PeerJ},
\emph{5}(e3644). \url{https://doi.org/10.7717/peerj.3644}

@@

\leavevmode\hypertarget{ref-Jeni2013FacImb}{}%
Jeni, L. A., Cohn, J. F., \& De La Torre, F. (2013). Facing Imbalanced
Data--Recommendations for the Use of Performance Metrics. \emph{2013
Humaine Association Conference on Affective Computing and Intelligent
Interaction}, 245--251. \url{https://doi.org/10.1109/ACII.2013.47}

@@

\leavevmode\hypertarget{ref-Martinez1992ConCon}{}%
Martinez, N. D. (1992). Constant Connectance in Community Food Webs.
\emph{The American Naturalist}, \emph{139}(6), 1208--1218.
\url{http://www.jstor.org/stable/2462337}

@@

\leavevmode\hypertarget{ref-Olesen2011MisFor}{}%
Olesen, J. M., Bascompte, J., Dupont, Y. L., Elberling, H., Rasmussen,
C., \& Jordano, P. (2011). Missing and forbidden links in mutualistic
networks. \emph{Proc. R. Soc. B}, \emph{278}(1706), 725--732.
\url{https://doi.org/10.1098/rspb.2010.1371}

\leavevmode\hypertarget{ref-Olito2015SpeTra}{}%
Olito, C., \& Fox, J. W. (2015). Species traits and abundances predict
metrics of plant--pollinator network structure, but not pairwise
interactions. \emph{Oikos}, \emph{124}, 428--436.

\leavevmode\hypertarget{ref-Pichler2020MacLea}{}%
Pichler, M., Boreux, V., Klein, A., Schleuning, M., \& Hartig, F.
(2020). Machine learning algorithms to infer trait‐matching and predict
species interactions in ecological networks. \emph{Methods in Ecology
and Evolution}, \emph{11}(2), 281--293.
\url{https://doi.org/10.1111/2041-210X.13329}

\leavevmode\hypertarget{ref-Pilosof2017MulNat}{}%
Pilosof, S., Porter, M. A., Pascual, M., \& Kéfi, S. (2017). The
multilayer nature of ecological networks. \emph{Nature Ecology \&
Evolution}, \emph{1}, 0101.
\url{https://doi.org/10.1038/s41559-017-0101}

@@

\leavevmode\hypertarget{ref-Poisot2021ImpMam}{}%
Poisot, T., Ouellet, M.-A., Mollentze, N., Farrell, M. J., Becker, D.
J., Albery, G. F., Gibb, R. J., Seifert, S. N., \& Carlson, C. J.
(2021). \emph{Imputing the mammalian virome with linear filtering and
singular value decomposition}. \url{http://arxiv.org/abs/2105.14973}

@@

\leavevmode\hypertarget{ref-Somodi2017PreDep}{}%
Somodi, I., Lepesi, N., \& Botta‐Dukát, Z. (2017). Prevalence dependence
in model goodness measures with special emphasis on true skill
statistics. \emph{Ecology and Evolution}, \emph{7}(3), 863--872.
\url{https://doi.org/10.1002/ece3.2654}

@@

\leavevmode\hypertarget{ref-Strona2017ForPer}{}%
Strona, G., \& Veech, J. A. (2017). Forbidden versus permitted
interactions: Disentangling processes from patterns in ecological
network analysis. \emph{Ecology and Evolution}, \emph{7}(14),
5476--5481. \url{https://doi.org/10.1002/ece3.3102}

@@

\leavevmode\hypertarget{ref-Valdovinos2019MutNet}{}%
Valdovinos, F. S. (2019). Mutualistic networks: Moving closer to a
predictive theory. \emph{Ecology Letters}, \emph{0}(0).
\url{https://doi.org/10.1111/ele.13279}

@@

\leavevmode\hypertarget{ref-Xie2017ComCom}{}%
Xie, J.-R., Zhang, P., Zhang, H.-F., \& Wang, B.-H. (2017). Completeness
of Community Structure in Networks. \emph{Scientific Reports},
\emph{7}(1), 5269. \url{https://doi.org/10.1038/s41598-017-05585-6}
